\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-12-12 response.tex

%%%%%%%%%%%%% Comment 1.1
\begin{cmt*}{}{}

	This paper proposes a multi-agent mobile robot planning algorithm that
	is robust agains attackers that would compromise the agents by
	directing them to unsafe regions. This is achieved by incorporating 1)
	co-observation constraints so that the agents could watch over each
	other, 2) reachability constraints so that the region the agents could
	potentially enter does no overlap with unsafe regions, and 3) sub-team
	planning algorithm to improve robustness by adding more number of
	agents.

	The proposed method is interesting, but I think the writing must be
	improved significantly to secure the clarity, and there are a lot of
	grammar mistakes that need to be fixed. To me, it appears that the
	draft may have been prepared somewhat hastily, which is not considerate
	of the reviewers' time.
	\tcblower
	\underline{\textbf{Response:}} We are grateful for your thoughtful comments and for expressing interest in our proposed method. We sincerely apologize for the grammatical mistakes in the initial submission and acknowledge the importance of presenting our work with clarity and professionalism. In the revised version, we have been extra careful to address all grammar issues and have implemented thorough proofreading to minimize similar mistakes in future submissions. We greatly appreciate your patience and constructive feedback, which have been invaluable in improving the quality of our manuscript.

\end{cmt*}
\vspace{0.1cm}
%%%%%%%%%%%%% Comment 1.0
\begin{cmt}{}{}        %% use * when do not need enumerate
	It seems like Example 1 is introduced as an example to help
	readers understand the formulation (1) in details. However, it is still
	vague, and it doesn't easily connect to Figure 3b.
	\tcblower
	\underline{\textbf{Response:}} Example 1 has been revised to improve clarity, with additional illustrative content and an updated figure added to better showcase the example application and its relevance to the proposed approach.
\end{cmt}
\rv
\begin{example}\label{example:map_exploration}
\new{Robots are tasked with navigating an unknown task space to collect sensory data and reconstruct a field (as illustrated in~\cref{fig:illustration}). The task space is modeled as a grid, where each grid point has an associated value tracked by a Kalman Filter (KF) [28]. The KF estimates uncertainty at each point through its covariance $P_j$ updated based on the measurements taken by robots along the trajectory $\vq$. Measurement quality, modeled by a Gaussian radial basis function, decreases with distance from the robot. The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty in reconstructing the field (detailed in [6]). }
\end{example}

\setcounter{figure}{1}
\begin{figure}[H]
	\centering
  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
  \caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case. (\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task. Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
\end{figure}
{\news Ideally, robots are expected to spread out in a Boustrophedon pattern to efficiently explore the task space, optimize coverage, and minimize reconstruction uncertainty (\cref{fig:SecurityBreak}). However, we consider the possibility of threats following the \emph{physical masquerade attack} model [2], where a compromised insider (robot) masquerading as a properly functioning agent, attempts to gain access to unauthorized locations without detection. The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE). These malicious deviations remain undetected as long as observations from uncompromised robots align with the motion plan. The corresponding security requirement can then be formally defined as:}
\begin{definition}\label{def:secured-plan}
  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots. 
\end{definition}

% {\news Ideally, robots are expected to spread out in a boustrophedon pattern to efficiently explore the task space, optimizing coverage and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}). To address potential threats, we adopt the \emph{physical masquerade attacks} framework from [2], where a compromised insider (robot) masquerading as a properly functioning robot, attempting to gain access to unauthorized locations without detection. The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE). These malicious deviations remain undetected as long as the self-reports from uncompromised robots align with the motion plan. The corresponding security requirement can then be formally defined as:}
% \begin{definition}\label{def:secured-plan}
%   A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots. 
% \end{definition}

@@

	Appendix, so that some space can be dedicated more to improve the
	clarity of the other sections.
	\tcblower
	\underline{\textbf{Response:}} As suggested, we have condensed this section and moved part of the “Transformation to Canonical Frame” section into the appendix to streamline the main text and improve readability. We believe that the remaining details on the implementation of the reachability constraints are essential and provide critical context for understanding the proposed method. We appreciate your suggestion, which has helped us enhance the balance and clarity of the manuscript. 

@@

\def\sZ{\mathcal{Z}}
\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint}
{\news  
The reachability constraint for a convex polygon is treated as a union of reachability constraints for each individual segments that define the hyperplane. We define

@@

\end{equation}
When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e. red region in Fig. 3d), the constraint is a plane-ellipse constraint in Section II-F. Otherwise (i.e. brown region in Fig. 3d), the constraint is a point-ellipse constraint in Section II-F.

\begin{constraint}[Line-segment-ellipsoid reachability constraint]
\begin{align}
D_{seg}(\vq) &=  \begin{cases}
D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
\end{cases} \label{eq:segment_ellipsoid_constraint}\\
  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D_{seg}(\vq)} = 0 \},\\
   \Pi_\sZ(\vz) & = 0, 
\end{align}
\end{constraint}
where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function (11) respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint (22). with respect to frame $\Eframe {\cL}$.
This constraint needs to be supplemented with a convex obstacle constraint for the polygon (i.e. keep foci waypoints outside the region, introduced in [6]) to prevent cases where the ellipse is a subset of the region.
}

\vspace{0.2cm}
%%%%%%%%%%%%% Comment 1.3
\begin{cmt}{}{}
	The word “checkpoint” appears abruptly in page 6 without concrete
	definition, although it seems like it is an important component of the
	formulation, and an important design choice for the results. For
	example, in the way Figure 3 is presented, I don't get a good idea why
	the checkpoint location is there in (c). 
	\re 
	\noindent
 For the feedback regarding the term "checkpoint", the original intent of “checkpoint” in Section 2 was to illustrate the limitations of the method proposed, specifically to show that even if APMAPF yields a valid solution, transforming this solution to a continuous domain may still need additional security measure to guarantee security. To address the concern, we have replaced the term “checkpoints” with “key locations” in Section 2 to avoid confusion. Additionally, we have added a formal definition of “checkpoints” and the “checkpoint graph” later in Section 3 to provide a clear and precise explanation of these concepts. These updates ensure that the term is used consistently and that its role in the methodology is explicitly defined. 
\end{cmt}
\rv
\renewcommand\thesubsection{H}
\subsection{Secured planning results and limitation}\label{sec:ADMM-simulation}
We employ the \new{Attack-Proof MAPF(APMAPF)} solver [2] on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.4a). This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task. Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions. Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions. {\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space. In this case, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids. Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated. For instance, in this scenario, we deploy a security camera as additional security measure to observe agent 3 at time $8$ to ensure security.}

@@

	For Figure 2, we appreciate the comment regarding the lack of a number scale especially on (b,c,d). The intention of these figures are to illustrate the geometric relationships between ellipsoids and different shapes, as well as the transformation of coordinates. To maintain focus on these aspects, we chose to omit the number scale and believe that it is not essential for conveying the intended concept.
\end{cmt}
\rv
\setcounter{figure}{1}
\begin{figure}[H]
	\centering
	\subfloat[\new{Map exploration task}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
	\subfloat[Continuous world trajectory\label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
	% \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
	\caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case. (\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task. Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
  \end{figure}
  \begin{figure}[H]
    \centering
    \subfloat[Showcase of a reachability region\label{fig:EllipseConstraintExample}]{\includegraphics[width=0.47\linewidth]{Reachability-v2}}
    \subfloat[Point-ellipsoid constraint \label{fig:Ellipse-to-point}]{\includegraphics[width=0.47\linewidth]{Ellipse2point-v2}}

    \subfloat[Plane-ellipse constraint \label{fig:Ellipse-to-plane}]{ \includegraphics[width=0.47\linewidth]{Ellipse2line-v3}}
    \subfloat[Polygon-ellipse constraint \label{fig:Ellipse-to-safezone}]{\includegraphics[width=0.47\linewidth]{Ellipse2safezone-v3}}

    \caption{\news (\ref{fig:EllipseConstraintExample}) The black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations where the robots are expected at given times $t_1$ and $t_2$, dashed lines show a possible trajectory of a compromised robot during the unobserved period. The axis of global frame $\cF$ and canonical frame $\cF_{\cE}$ are shown as $x_{\cF}, y_{\cF}$ and $x_{\cE}, y_{\cE}$ respectively. 
    (\ref{fig:Ellipse-to-point}) For point-ellipsoid constraint, $q_{avoid}$ is projected to the areas outside the ellipsoid to $q_{p}$. 
    (\ref{fig:Ellipse-to-plane}) For plane-ellipsoid constraint, the projection is simplified to the point-ellipse constraint that projects point $p_{L}$ outside the ellipse to $p_{t}$.
    (\ref{fig:Ellipse-to-safezone}) For convex-polygon-ellipsoid constraint, the projection is either a plane-ellipse constraint $D_{1}$ (for the red region) or a point-ellipse constraint $D_{2}$ (for the brown region).}
    \label{fig:Reachability_full}
  \end{figure}
  \begin{figure}[H]
	\centering
  % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
  \subfloat[\new{Grid world result}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
  % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
  \subfloat[Secured result. \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,valign=t]{FinalResult-v2}}
  \caption{{\news Trajectory design of a three-robot system based on the grid world result. Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions. (\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective. (\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints. Attack attempts into the forbidden region (red dashed line) will cause team 1 miss the next scheduled co-observation.}}
  \label{fig:example-application}
  \end{figure}
  \setcounter{figure}{6}
  \begin{figure}[H]
	\centering
	\subfloat[Cross-trajectory co-observation plan \label{fig:previous_result_plan}]{\includegraphics[width=0.4\linewidth, trim = 2cm 1cm 1cm 1cm,clip,valign=b]{old_result_v2}}
	\subfloat[Checkpoint graph and result flows \label{fig:previous_result_graph}]{\includegraphics[width=0.4\linewidth, trim = 10cm 3cm 7cm 3cm,clip,valign=b]{old_result_graph_v2}}
	\caption{\new{(\ref{fig:previous_result_plan}) The cross-trajectory co-observation plan is shown as arrows on top of the original plan in \cref{fig:previous_result_plan}. (\ref{fig:previous_result_graph}) The checkpoint graph and resulting flows highlighted.}}
	\label{fig:3-team-ctco}
  \end{figure}

@@

  \begin{figure}[H]
	\centering
	%\subfloat[Unsecured plan\label{fig:unsecured-plan}]{\includegraphics[width=0.31\linewidth, trim = 3cm 2cm 3cm 2cm, clip,valign=c]{SecurityBreak}}
	\subfloat[4-agent case\label{fig:Result-plan}]{\includegraphics[width=0.4\linewidth,trim = 1cm 1cm 1.5cm 0cm, clip,valign=c]{Traj_result_v3.png}}
	%\subfloat[Graph flow result\label{fig:result-graph}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{Graph_result}}
	\subfloat[7-agent case\label{fig:Result-plan-7-team}]{\includegraphics[width=0.4\linewidth,trim = 3.5cm 2cm 1.5cm 0cm, clip,valign=c]{7-team-plan_v2.png}}
	%\subfloat[Graph flow result\label{fig:result-graph-7-team}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{7-team-graph.png}}
	\caption{\new{(\ref{fig:Result-plan}) Cross-trajectory co-observation result of a 4 sub-teams task. (\ref{fig:Result-plan-7-team}) Cross-trajectory co-observation result of a 7 sub-teams task.}}\label{fig:Cross-trajectory-result}
  \end{figure}
\vspace{0.2cm}

\begin{cmt}{}{}
	The author assumes “Zone 1” is tolerable and Zone 2 and 3 are hard
constraints, but what if the environment is the opposite? Do you get
infeasible solution? It is very skeptical that the author is making
deliberate assumptions to make the example work in a special case.
\re We acknowledge the limitation of the method proposed in Section II, as it relies on the specific setup, and a safe solution is not always guaranteed to exist. This limitation is explicitly discussed in the manuscript. The chosen result is deliberate, not to make the example work in a special case, but to illustrate that even when APMAPF finds a solution in the grid world, such a plan may fail to guarantee security when transformed into the continuous domain, requiring further manual adjustments. In the revised version, we have further emphasized these limitations and the challenges they aim to address in the simulation results.
\end{cmt}
\vspace{0.1cm}
\rv
\renewcommand\thesubsection{H}
\subsection{Secured planning results and limitation}\label{sec:ADMM-simulation}
We employ the \new{Attack-Proof MAPF(APMAPF)} solver [2] on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.4a). This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task. Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions. Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions. {\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space. In this case, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids. Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated. For instance, in this scenario, we deploy a security camera as additional security measure to observe agent 3 at time $8$ to ensure security.}

### 2024-12-12 paper.tex
Finished

    \caption{{\news \ref{fig:example-plan-dev} The attacker deviates the red robot into a forbidden region.\ref{fig:example-co-observation} Red and blue robots are scheduled to co-observe each other during the task, resulting in a new secured trajectory (solid lines) replacing the optimal ones (dashed line). \ref{fig:example-cross-traj} The blue team sends one robot to observe the red team (solid blue line) while having the rest of the robots follow the optimal trajectory.}\label{fig:cross-traj-comparison-set}}
\end{figure}

@@

\begin{example}\label{example:map_exploration}
\new{Robots are tasked with navigating an unknown task space to collect sensory data and reconstruct a field (as illustrated in~\cref{fig:illustration}). The task space is modeled as a grid, where each grid point has an associated value tracked by a Kalman Filter (KF) \cite{anderson2012optimal}. The KF estimates uncertainty at each point through its covariance $P_j$ updated based on the measurements taken by robots along the trajectory $\vq$. Measurement quality, modeled by a Gaussian radial basis function, decreases with distance from the robot. The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty in reconstructing the field (detailed in \cite{yang2020multi}). }
\end{example}
\begin{figure}
  \centering
  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
  \caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case. (\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task. Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
\end{figure}

@@

For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):%$\mathcal{E}=\{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)<v_{max}(t_2-t_1)\}$, where $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
\begin{definition}\label{def:Reachability}
	The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$, and $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
\end{definition}
This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid. }
 \begin{figure}
    \centering
    \subfloat[Showcase of a reachability region\label{fig:EllipseConstraintExample}]{\includegraphics[width=0.47\linewidth]{Reachability-v2}}
    \subfloat[Point-ellipsoid constraint \label{fig:Ellipse-to-point}]{\includegraphics[width=0.47\linewidth]{Ellipse2point-v2}}

@@

% \begin{constraint}[Line-segment-ellipsoid reachability constraint]
% \begin{align}
% D(\vq) &=  \begin{cases}
% D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
% D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
% D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
% \end{cases} \label{eq:segment_ellipsoid_constraint}\\
%   \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
%    \Pi_\sZ(\vz) & = 0, 
% \end{align}
% \end{constraint}
% where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint}. with respect to frame $\Eframe {\cL}$.
\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint}
{\news  
The reachability constraints for a convex polygon is treated as a union of reachability constraints for each individual segments that define the hyperplane. We define
\begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
\begin{align}
D(\vq) &= \bmat{D_{seg1}(\vq)\\D_{seg2}(\vq)\\ \vdots} \label{eq:region_ellipsoid_constraint}\\
  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
   \Pi_\sZ(\vz) & = 0, 
\end{align}
\end{constraint}
where $D_{seg}$ are the constraint functions for all line segments that define the convex polygon region. 
For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:
\begin{equation}
\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
\end{equation}
When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e. red region in \cref{fig:Ellipse-to-safezone}), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}. Otherwise (i.e. brown region in \cref{fig:Ellipse-to-safezone}), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.

\begin{constraint}[Line-segment-ellipsoid reachability constraint]
\begin{align}
D_{seg}(\vq) &=  \begin{cases}
D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
\end{cases} \label{eq:segment_ellipsoid_constraint}\\
  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D_{seg}(\vq)} = 0 \},\\
   \Pi_\sZ(\vz) & = 0, 
\end{align}
\end{constraint}
where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint}. with respect to frame $\Eframe {\cL}$.
This constraint needs to be supplemented with a convex obstacle constraint for the polygon (i.e. keep foci waypoints outside the region, introduced in \cite{yang2020multi}) to prevent cases where the ellipse is a subset of the region.
}
\subsection{Secured planning results and limitation}\label{sec:ADMM-simulation}
%All robots are tasked with collecting sensor information on the vector field, with higher accuracy of sensor data for locations closer to the agent. %robots are expected to follow a boustrophedon pattern (similar to the unconstrained result in Figure~\ref{fig:SecurityBreak}). %We apply the new security constraints on the map exploration problem shown in \cref{fig:example-application}, test the algorithm in both simulations and an experimental testbed. The 3-robot system is tasked to explore a $10m\times10m$ region with two forbidden regions \emph{Zone 2, 3}. The maximum velocity constraint $v_{max}$ is set to~$0.5m/dt$ a time limit of 20.

>>>>

    \caption{{\news (\ref{fig:example-plan-dev}) The attacker deviates the red robot into a forbidden region.(\ref{fig:example-co-observation}) Red and blue robots are scheduled to co-observe each other during the task, resulting in a new secured trajectory (solid lines) replacing the optimal ones (dashed line). (\ref{fig:example-cross-traj}) The blue team sends one robot to observe the red team (solid blue line) while having the rest of the robots follow the optimal trajectory.}\label{fig:cross-traj-comparison-set}}
\end{figure}

@@

\begin{example}\label{example:map_exploration}
\new{Robots are tasked with navigating an unknown task space to collect sensory data and reconstruct a field (as illustrated in~\cref{fig:illustration}). The task space is modeled as a grid, where each grid point has an associated value tracked by a Kalman Filter (KF) \cite{anderson2012optimal}. The KF estimates uncertainty at each point through its covariance $P_j$ updated based on the measurements taken by robots along the trajectory $\vq$. Measurement quality, modeled by a Gaussian radial basis function, decreases with distance from the robot. The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty in reconstructing the field (detailed in \cite{yang2020multi}). }
\end{example}
\begin{figure}
  \centering
  \subfloat[\new{Map exploration task}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
  \caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case. (\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task. Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
\end{figure}

@@

For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):%$\mathcal{E}=\{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)<v_{max}(t_2-t_1)\}$, where $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
\begin{definition}\label{def:Reachability}
	The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$, and $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
\end{definition}
This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where $a$ is the major radius of the ellipsoid. }
 \begin{figure}
    \centering
    \subfloat[Showcase of a reachability region\label{fig:EllipseConstraintExample}]{\includegraphics[width=0.47\linewidth]{Reachability-v2}}
    \subfloat[Point-ellipsoid constraint \label{fig:Ellipse-to-point}]{\includegraphics[width=0.47\linewidth]{Ellipse2point-v2}}

@@

% \begin{constraint}[Line-segment-ellipsoid reachability constraint]
% \begin{align}
% D(\vq) &=  \begin{cases}
% D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
% D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
% D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
% \end{cases} \label{eq:segment_ellipsoid_constraint}\\
%   \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
%    \Pi_\sZ(\vz) & = 0, 
% \end{align}
% \end{constraint}
% where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint}. with respect to frame $\Eframe {\cL}$.
\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint}
{\news  
The reachability constraint for a convex polygon is treated as a union of reachability constraints for each individual segments that define the hyperplane. We define
\begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
\begin{align}
D(\vq) &= \bmat{D_{seg1}(\vq)\\D_{seg2}(\vq)\\ \vdots} \label{eq:region_ellipsoid_constraint}\\
  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
   \Pi_\sZ(\vz) & = 0, 
\end{align}
\end{constraint}
where $D_{seg}$ are the constraint functions for all line segments that define the convex polygon region. 
For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:
\begin{equation}
\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
\end{equation}
When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e. red region in \cref{fig:Ellipse-to-safezone}), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}. Otherwise (i.e. brown region in \cref{fig:Ellipse-to-safezone}), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.

\begin{constraint}[Line-segment-ellipsoid reachability constraint]
\begin{align}
D_{seg}(\vq) &=  \begin{cases}
D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
\end{cases} \label{eq:segment_ellipsoid_constraint}\\
  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D_{seg}(\vq)} = 0 \},\\
   \Pi_\sZ(\vz) & = 0, 
\end{align}
\end{constraint}
where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint} with respect to frame $\Eframe {\cL}$.
This constraint needs to be supplemented with a convex obstacle constraint for the polygon (i.e. keep foci waypoints outside the region, introduced in \cite{yang2020multi}) to prevent cases where the ellipse is a subset of the region.
}
\subsection{Secured planning results and limitation}\label{sec:ADMM-simulation}
%All robots are tasked with collecting sensor information on the vector field, with higher accuracy of sensor data for locations closer to the agent. %robots are expected to follow a boustrophedon pattern (similar to the unconstrained result in Figure~\ref{fig:SecurityBreak}). %We apply the new security constraints on the map exploration problem shown in \cref{fig:example-application}, test the algorithm in both simulations and an experimental testbed. The 3-robot system is tasked to explore a $10m\times10m$ region with two forbidden regions \emph{Zone 2, 3}. The maximum velocity constraint $v_{max}$ is set to~$0.5m/dt$ a time limit of 20.
